While I am incredibly grateful to so many people who have supported me throughout my PhD journey, I have never been very good at expressing my gratitude in words. For this reason, as I write this section, I realize that one of the things I am grateful for is this very thesis for prompting me to take the time to express feelings that too often go unspoken. This process has allowed me to reflect on the incredible support and encouragement that I have received from so many people, and has reminded me of how fortunate I am to have such wonderful friends, family, colleagues, and mentors in my life.

The first people I would like to thank are the members of my jury for their valuable comments and insightful feedback during the revision and the defense of my thesis. Their constructive criticism and suggestions have been immensely helpful in improving the quality and clarity of my work. Without their guidance during the pre-defense of my thesis this dissertation would not be what it is today.

My deep gratitude goes to my supervisors, Remzi Sanver and Olivier Cailloux, for their unwavering support, advice, and encouragement throughout my research journey. Remzi’s expertise, mentorship, and willingness to share knowledge have been instrumental in shaping the direction of my research. Olivier’s dedication to work, guidance and attention to details have contributed in shaping who I am today as a researcher but also as a person. Olivier, even though I may have rolled my eyes at times, I will never forget your meticulous comments, jokes and our insightful discussions. Your words of encouragement, constructive feedback and your confidence in my abilities have been a source of motivation and inspiration, even during the most challenging times. Thank you both for being there even when I did not know I needed you.

I would also like to extend my appreciation to all the PhD students in our lab for creating such a positive and collaborative atmosphere. Most of these past few years have been marked by a pandemic that disrupted all of our lives and we have not been able to take advantage of the classical social events. However, this has not prevented the growth of important relationships and deep friendships that I hope will continue in the future. I also thank all the members of LAMSADE, including professors and administrative staff, for the warm welcome I received when I joined the lab. I feel grateful to have had the opportunity to work alongside such an amazing group of people.

I am especially grateful to Jérôme Lang, for helping me during a tough time when he himself was going through a very hard moment in his life. His generosity and kindness have been invaluable and I will never be able to fully express my gratitude.

Although I never told him, I would also like to thank Umberto Grandi, for responding to a stranger’s email in the middle of the summer of some years ago asking for an internship for the following week. I consider this event as the sliding doors moment of my life. Umberto has been extremely kind and welcoming, taught me the fundamentals of a field that was completely new to me until then, and believed in me and supported me from the beginning. This opportunity not only allowed me to gain valuable experience and skills but also opened the door for my PhD. Moreover, it allowed me to get to know the person who, years later, became my life partner.

Perhaps the greatest thanks goes to this very person, my partner in crime, my soulmate. Arthur, your   presence in my life has been a constant source of comfort and strength, I am grateful for your love and patience during the most challenging times. You are my number one fan, my best supporter. 
You have stood by my side through the ups and downs, always offering a shoulder to lean on and you pushed me to keep going, even when I felt like giving up. I feel incredibly lucky to have you in my life. Thank you for being such an amazing partner and for always having my back. Thank you for being you.

Finally, I would like to express my deepest gratitude to my family and friends for their love, encouragement, and understanding during this challenging yet rewarding period of my life. Their support and belief in me have been a constant source of motivation and inspiration. Thanks to the old friends who have always stood by my side despite kilometers of distance, friendships made up of texts and video calls. Friendships where you don't hear from each other for weeks but a phone call is enough to shorten time and distance. Friendships made up of venting and support but also laughter and memes. Thanks to the new friends, who became my Parisian family since we met the first week I set foot in this new city. The friends who bring you a hot meal when you are sick and who come to help you move even when you don't ask them to. Thanks to my acquired family, Arthur's parents and siblings, who welcomed me into their family with open arms. Their kindness, warmth, and generosity have made me feel like a part of the family from the very beginning and they have shown me nothing but love and support. 

And, last but not least, thanks to my family. Their sacrifices and support, have allowed me to pursue my dreams and achieve milestone after milestone in my academic career. Every departure has been heartbreaking, but my family has always been the first to encourage me to follow my ambitions. The packages that they periodically send from Cosenza to Paris are full of coffee, chocolate and sausages only to the outside eye, but in reality they are primarily full of love. I feel grateful and blessed to have such a wonderful family who have always been there for me, no matter the distance. Thank you for being my rock and my foundation, and for making me the person I am today. 